proof-of-concept_mods

### 2023-11-15 proof-of-concept_mods.Rmd

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(gamlss, gamlss.cens, gamlss.dist, gamlss.mx, gamlss.tr, ggplot2, tidyverse, ggpubr, skimr, gamlss.data, data.table, nlme, devtools, slider, tidymodels, broom.mixed, ggseg, cowplot, lsr, paletteer)

source("./R_scripts/gamlss_helper_funs.R")
```

@@

@@

@@

>>>>

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(gamlss, gamlss.cens, gamlss.dist, gamlss.mx, gamlss.tr, ggplot2, tidyverse, ggpubr, skimr, gamlss.data, data.table, nlme, devtools, slider, tidymodels, broom.mixed, ggseg, cowplot, lsr, paletteer, ggsegExtra, ggseg3d)

source("./R_scripts/gamlss_helper_funs.R")
# 
# # Enable this universe
# options(repos = c(
#   ggseg = 'https://ggseg.r-universe.dev',
#   CRAN = 'https://cloud.r-project.org'))
# 
# # Install some packages
# install.packages('ggsegExtra')
```

@@

Simple bar plot of sites
```{r}
ggplot(ukb_df_age.filt) +
  geom_bar(aes(x=sim.site, fill=sex), color="black", alpha=0.6) +
  theme_linedraw(base_size=12)
```

@@

using aseg

```{r}
plot(aseg)
```

@@

```{r}
sigma.aseg_all <- sigma.df %>%
  dplyr::filter(pheno_cat == "Global Volume" & term =="sexMale") %>%
  filter(!str_detect(dataset, "-refA")) %>%
  dplyr::select(!label) %>%
  mutate(dataset = factor(dataset, levels = c("ukb-CN-simsites", "cf", "cf.lm", "cf.gam", "cf.gamlss")),
         tissue_class = as.factor(case_when(pheno == "GMV" ~ "cGM",
                                            pheno == "Ventricles" ~ "CSF",
                                            pheno == "WMV" ~ "White Matter",
                                            pheno == "sGMV" ~ "sGM",
                                            TRUE ~ NA)),
         var_est = case_when(sig.sum_bf.corr == TRUE ~ var_est,
                             TRUE ~ NA)) #just keep significant regions

sigma.aseg_all <- left_join(sigma.aseg_all, aseg_cerebrum$data, by = c("tissue_class"))

sigma.aseg_all %>%
  group_by(dataset) %>%
  ggplot() +
  geom_brain(atlas = aseg_cerebrum, 
             #position = position_brain(hemi ~ side),
             aes(fill = var_est),
             alpha=0.8) +
  #scale_fill_gradient2() +
  facet_wrap(~dataset) + 
  theme_bw(base_size=20) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA)) +
  paletteer::scale_fill_paletteer_c("grDevices::Oslo") +
  ggtitle("Beta weight for effect of male sex on variance")
```
